Analysis paper

### 2021-05-03 analysis/analysis.Rmd
update plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(covid.german.forecasts)
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
```

@@

```{r truth-vs-forecasts, fig.height=10, fig.width=15}
# load unfiltered combined data 
df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
                      grepl("2", target) & 
                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
df[, location_target := paste0(target_type, "s", " in ", location_name)]

@@

```{r fig.height=10, fig.width=15}
# glue two plots together
truth_vs_forecast_2 | rel_skill_time_2 + 
  plot_layout(guides = "collect") & 
  theme(legend.position = 'bottom') 
ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
```
*Figure 1. Left: Visualisation of 2 week ahead forecasts against the true observed values. The shape indicates whether there has been a monotonic increase or decrease over the last two weeks, or an unclear trend. Forecasts made during the Christmas period (from 2020-12-19 until 2021-01-02) are grayed out. Right: Corresponding scaled relative skill scores for the forecasts shown on the left. Scaled relative skill scores can be thought of as 'improvement over the baseline model' (see Methods for details).*

@@

```{r}
p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_brewer(palette = "Accent") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

```{r}
# scores for different phases of the epidemic
scores[, target_phase := paste0(target_type, "s - ", classification, " phase")]
p_phases <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_brewer(palette = "Accent") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_phase) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

@@

p / p_phases + 
  plot_layout(guides = "collect") & 
  theme(legend.position = 'bottom')

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(covid.german.forecasts)
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
```

@@

```{r truth-vs-forecasts, fig.height=10, fig.width=15}
# load unfiltered combined data 
df <- combined_data[as.Date(forecast_date) %in% forecast_dates$unfiltered &
                      grepl("2", target) & 
                      quantile %in% c(0.025, 0.25, 0.75, 0.975)]
df[, location_target := str_to_title(paste0(target_type, "s", " in ", location_name))]

@@

```{r fig.height=10, fig.width=15}
# glue two plots together
truth_vs_forecast_2 | rel_skill_time_2 +
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

# for some reason the A / B annotation doesn't work here

ggsave(here("analysis", "plots", "figure-forecasts-2.png"))
```
*Figure 1. Left: Visualisation of 2 week ahead forecasts against the true observed values. The shape indicates whether there has been a monotonic increase or decrease over the last two weeks, or an unclear trend. Forecasts made during the Christmas period (from 2020-12-19 until 2021-01-02) are grayed out. Right: Corresponding scaled relative skill scores for the forecasts shown on the left. Scaled relative skill scores can be thought of as 'improvement over the baseline model' (see Methods for details).*

@@

```{r}
p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

```{r}
# scores for different phases of the epidemic
scores[, target_phase := str_to_title(paste0(target_type, "s - ", 
                                             classification, " phase"))]
scores[, target_phase := factor(target_phase, 
                                levels = str_to_title(c("Cases - decreasing phase", 
                                                        "Cases - unclear phase", 
                                                        "Cases - increasing phase", 
                                                        "Deaths - decreasing phase", 
                                                        "Deaths - unclear phase", 
                                                        "Deaths - increasing phase")))]

scores[, .(target_count = .N), by = c("target_phase")]

p_phases <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_phase) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

@@

p / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

@@

```{r, eval = TRUE}
scores <- eval_forecasts(
  data[, horizon := substring(target, 1, 1)], 
  summarise_by = c("model", "target_type", "location_name", "horizon"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

scores %>%
  ggplot(aes(y = interval_score, x = horizon, color = model, 
             group = model)) + 
  geom_point() + 
  geom_line() + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_color_brewer(palette = "Accent") + 
  scale_y_log10() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")
